Symmetric Circuits for Rank Gates

### 2018-02-28 sections/transparency-and-unique-extensions.tex
Updates to the entire paper 28th Feb 2018

\begin{lem}
  There is an algorithm that takes as input a transparent circuit $C$ and
  outputs the syntactic-equivalence relation on the gates of $C$. The algorithm
  runs in time polynomial in the size of $C$.
  \label{lem:unique-labels-syntactic-equiv}
\end{lem}
\begin{proof}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
  $(\mathbb{B}, \rho)$-circuit of order $n$. We define the syntactic-equivalence
  relation on $G$ by induction on the height of a gate We note that this
  definition can be implemented by a dynamic program.

  Suppose $g$ and $h$ are gates in $C$ such that $\Sigma (g) = \Sigma(h)$ and
  either both $g$ and $h$ are output gates and $\Omega^{-1}(g) = \Omega^{-1}(h)$
  or neither are output gates. Let $g$ and $h$ be input gates, then set $g
  \equiv h$ if, and only if, both $g$ and $h$ are constant gates or both are
  relational gates and $\Lambda(g) = \Lambda (h)$. Let $g$ and $h$ be internal
  gates and suppose we have defined the syntactic-equivalence relation for all
  gates of height less than the height of either $g$ or $h$. Then $g \equiv h$
  if, and only if, $L(g)$ and $L(h)$ are isomorphism equivalent up to $\equiv$.

@@

  Let $g$ and $h$ be two internal gates in $C$ and suppose we have defined the
  syntactic-equivalence relation for all gates of height less than the height of
  either $g$ or $h$. We test if for each gate in $g' \in H_g$, there exists
  $h_{g'} \in H_h$ such that $g' \equiv h_{g'}$ and $\vert \{g'' \in H_g : g''
  \equiv g'\} \vert = \vert \{h'' \in H_h : h'' \equiv h'\}$. If this test
  fails, we set $g \not\equiv h$.

@@

We now prove that transparent circuits can be transformed in polynomial time
into equivalent circuits with unique extensions, and that this transformation
preserves important properties of the circuit.

\begin{lem}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
  $(\mathbb{B}, \rho)$-circuit. There is an algorithm that that takes in such a
  circuit and outputs a $(\mathbb{B} \cup \mathbb{B}_{\std}, \rho)$-circuit $C'$
  such that $C$ and $C'$ compute the same function, $C'$ has unique labels, and
  if $C$ is symmetric then $C'$ is symmetric. Moreover, this algorithm runs in
  time polynomial in the size of the input circuit.
  \label{lem:transparent-unique}
\end{lem}
\begin{proof}
  Let $C' := \op{make-injective-all}(\op{merge-all} (C, G))$ (see
  Definition~\ref{def:make-injective} and~\ref{def:merge-all} for the
  definitions of these functions). It follows that if $C$ is symmetric then $C'$
  is symmetric. We have from Lemma~\ref{lem:unique-labels-syntactic-equiv} that
  the syntactic-equivalence relation can be computed in polynomial time for
  transparent circuits. It follows that the construction of $C'$ from $C$ can be
  implemented so as to run in time polynomial in the size of $C$. Clearly every
  gate $g$ in $C'$ belongs to a singleton syntactic-equivalence equivalence
  class, and as such $C'$ has unique labels.
\end{proof}
% GW: read this when fresh

We now show that it is possible to compute the action of $\sym_n$ on the gates
of a circuit of order $n$ with unique labels in polynomial time. Recall that
from Proposition~\ref{prop:transparent-unique} we may, without a loss of
generality, restrict of attention from transparent circuits to circuits with
unique labels. The proof technique used here is similar to the one used by
Anderson and Dawar~\cite{AndersonD17}.

>>>>

\begin{lem}
  There is an algorithm that takes as input a transparent circuit $C$ and
  outputs the syntactic-equivalence relation on the gates of $C$. The algorithm
  runs in time polynomial in the size of $C$.
  \label{lem:transparent-syntactic-equiv}
\end{lem}
\begin{proof}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
  $(\mathbb{B}, \rho)$-circuit of order $n$. We define the syntactic-equivalence
  relation on $G$ by induction on the depth of a gate We note that this
  definition by induction can be implemented as a construction using a dynamic program.

  Suppose $g$ and $h$ are gates in $C$ such that $\Sigma (g) = \Sigma(h)$ and
  either both $g$ and $h$ are output gates and $\Omega^{-1}(g) = \Omega^{-1}(h)$
  or neither are output gates. Let $g$ and $h$ be input gates, then set $g
  \equiv h$ if, and only if, both $g$ and $h$ are constant gates or both are
  relational gates and $\Lambda(g) = \Lambda (h)$. Let $g$ and $h$ be internal
  gates and suppose we have defined the syntactic-equivalence relation for all
  gates of depth less than the depth of either $g$ or $h$. Then $g \equiv h$
  if, and only if, $L(g)$ and $L(h)$ are isomorphism equivalent up to $\equiv$.

@@

  Let $g$ and $h$ be two internal gates in $C$ and suppose we have defined the
  syntactic-equivalence relation for all gates of depth less than the depth of
  either $g$ or $h$. We test if for each gate in $g' \in H_g$, there exists
  $h_{g'} \in H_h$ such that $g' \equiv h_{g'}$ and $\vert \{g'' \in H_g : g''
  \equiv g'\} \vert = \vert \{h'' \in H_h : h'' \equiv h'\}$. If this test
  fails, we set $g \not\equiv h$.

@@

It is sometimes useful to define one circuit from another circuit by
\emph{quotienting} a circuit by the syntactic equivalence relation. Intuitively,
a quotient circuit is defined by `merging' each syntactic-equivalence class into
a single gate and including a wire between two gates in the quotient circuit if,
and only if, there is a wire between an element of each equivalence class.

\begin{definition}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a $(\BB,
  \rho)$-circuit. A \emph{quotient of $C$} is a $(\BB, \rho)$-circuit $C_\equiv
  := \langle G_\equiv , \Omega_\equiv, \Sigma_\equiv , \Lambda_\equiv, L_\equiv
  \rangle$, where $G_\equiv = G /_\equiv$, $\Omega_\equiv = \Omega /_\equiv$,
  $\Sigma = \Sigma /_\equiv$, $(\Lambda_\equiv)_R = \Lambda_R /_\equiv$ for all
  $R \in \rho$, and for all $[g] \in G_\equiv$ there exists $g' \in [g]$ such
  that, $L_\equiv$ associates with $[g]$ a function $L_\equiv([g]) : \ind(g')
  \rightarrow G_\equiv$ where $L_\equiv([g]) = L(g')/_\equiv$.
\end{definition}

We now show that taking the quotient of a circuit preserves important
properties, including the function computed by the circuit, whether the circuit
is symmetric, and has unique unique labels. We also show that the quotient of a
circuit has trivial syntactic-equivalence classes, and hence unique extensions.

\begin{lem}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\BB,
  \rho)$-circuit of order $n$ and $C_{\equiv} = \langle G_\equiv ,
  \Omega_\equiv, \Sigma_\equiv , \Lambda_\equiv, L_\equiv \rangle$ be a quotient
  of $C$. Then $C$ and $C_{\equiv}$ compute the same function and each
  syntacitic-equivalence class in $C_\equiv$ is a singleton. Moreover, if $C$ is
  symmetric then $C_{\equiv}$ is symmetric, and for all $g \in G$, $g$ has
  unique labels in $C$ if, and only if, $[g]$ has unique labels in $C_{\equiv}$.
  \label{lem:quotient-circuits-preserve}
\end{lem}
\begin{proof}
  We first prove that $C_\equiv$ and $C$ compute the same function. Let
  $\mathcal{A}$ be a $\rho$-structure of size $n$ and let $\gamma$ be a
  bijection from $U$ to $[n]$. We now show that for all $g \in G$, $C_\equiv
  [\gamma \mathcal{A}]([g]) = C[\gamma \mathcal{A}](g)$. We do this by induction
  on the depth of a gate. Suppose $g \in G$ has depth $0$. In this case $g$ is
  an input gate and the result follows trivially. Suppose $g$ is an internal
  gate and suppose for all $h$ of depth less than $g$ we have that
  $C_\equiv[\gamma \mathcal{A}]([h]) = C[\gamma \mathcal{A}](h)$. We have that
  there exists $g' \in [g]$ such that $L_\equiv ([g]) = L(g') /_\equiv$ and
  $\Sigma_\equiv([g]) = \Sigma (g) = \Sigma (g')$. We have from Lemma~\ref{} and
  the inductive hypothesis that there exists $\lambda \in \aut(g)$ such that
  $L_\equiv ([g]) = L(g') = L(g) \lambda$. It follows from the fact that
  $\Sigma(g)$ is a structured function that $C_\equiv[\gamma \mathcal{A}]([g]) =
  \Sigma_\equiv ([g])(L^{\gamma \mathcal{A}}_\equiv([g])) = \Sigma (g')
  (L^{\gamma \mathcal{A}}(g')) = \Sigma (g)(L^{\gamma \mathcal{A}}(g) \lambda) =
  \Sigma (g) (L^{\gamma \mathcal{A}}(g)) = C[\gamma \mathcal{A}](g)$.

  We now show that each syntactic-equivalence class in $C_\equiv$ is a
  singleton. Suppose $[g], [h] \in G_\equiv$ and suppose $[g] \equiv [h]$. If
  $[g]$ and $[h]$ are both input or output gates then $[g] = [h]$. Suppose $[g]$
  and $[h]$ are internal gates that are not output gates. Then $\Sigma (g) =
  \Sigma_\equiv ([g]) = \Sigma_\equiv([h]) = \Sigma(h)$. There exists $g', h'
  \in G$ such that $g' \equiv g$ and $h' \equiv h$, and $L_\equiv ([g]) = L(g')
  /_\equiv$ and $L_\equiv ([h]) = L(h') /_\equiv$. It follows from $[g] \equiv
  [h]$ that $L(g') /_\equiv$ is isomorphism-equivalent to $L(h') /_\equiv$. It
  follows that $g' \equiv h'$, and so $[g] = [h]$.

  We now show that if $C$ is symmetric then $C_\equiv$ is symmetric. Suppose $C$
  is symmetric. Let $\sigma \in \sym_n$. Then there exists $\pi \in \aut(C)$
  that extends $\sigma$. Let $\pi_\equiv = pi /_\equiv$. We now show that
  $\pi_\equiv$ is an automorphism of $C_\equiv$ extending $\sigma$. It is easy
  to see that $\pi_\equiv$ is a bijection from $G_\equiv$ to $G_\equiv$ that
  preserves syntactic-equivalence, and is thus is a well-defined function. Let
  $[g] \in G_\equiv$. We have that $\Sigma_\equiv (\pi_\equiv [g]) =
  \Sigma_\equiv ([\pi g]) = \Sigma (\pi g) = \Sigma (g) = \Sigma_\equiv ([g])$.
  It is easy to check the automorphism conditions for input gates. Suppose $[g]$
  is an internal gate. Let $g' \in [g]$ be such that $L_\equiv([g]) = L(g')
  /_\equiv$ and $h \in [g]$ be such that $L_\equiv(\pi_\equiv[g]) = L_\equiv
  ([\pi h]) = L(\pi h) /_\equiv$. We have that $\pi L(g')$ is
  isomorphism-equivalent to $L(\pi g')$, and it follows that $(\pi
  L(g'))/_\equiv$ is isomorphism-equivalent to $L(\pi g') /_\equiv$. We then
  have $(\pi L(g'))/_\equiv = \pi_\equiv (L(g') /_\equiv) = \pi_\equiv L_\equiv
  ([g])$ and, since $g' \equiv h$ and so $\pi g' \equiv \pi h$, we have that
  $L(\pi g')/_\equiv$ is isomorphism-equivalent to $L(\pi h) /_\equiv =
  L_\equiv(\pi_\equiv[g])$. It follows that $\pi_\equiv L_\equiv ([g])$ is
  isomorphism-equivalent to $L_\equiv(\pi_\equiv [g]) /_\equiv$. Suppose $[g]$
  is an output gate. Then for $\vec{a} \in \dom (\Omega)$, $\pi_\equiv
  \Omega_\equiv (\vec{a}) = [\pi \Omega (\vec{a})] = [\Omega (\sigma \vec{a})] =
  \Omega_\equiv (\sigma \vec{a})$.

  Let $g \in G$. Suppose $[g]$ has unique labels. There exists $h \in [g]$ such
  that $L_\equiv([g]) = L(h) /_\equiv$. Since $L_\equiv([g])$ is injective,
  $L(h) /_\equiv$ must be injective and so $L(h)$ must be injective and no two
  child gates of $L(h)$ must be syntactically-equivalent. It follows that $h$
  has unique labels. Since $h \equiv g$ and $h$ has unique labels, it follows
  that $g$ has unique labels. Suppose $g$ has unique labels. Let $h \in [g]$ be
  such that $L_\equiv([g]) = L(h) /_\equiv$. Since $h \equiv g$ and $g$ has
  unique labels $h$ has unique labels and so $L_\equiv([g])$ has injective
  labels. Since each equivilence class in $C_\equiv$ is a singlton it follows
  that $[g]$ has unique labels.

  % If $[g]$ is an input gate then $\pi_\equiv [g] = [\pi g]$, and

  % Let $\mathcal{A}$ be a $\rho$-structure of size $n$ and let $\gamma$ be a
  % bijection from $U$ to $[n]$. We have from Lemma~\ref{} that for all $g, g'
  % \in
  % G$, if $g \equiv g'$ then $C[\gamma \mathcal{A}](g) = C[\gamma
  % \mathcal{A}](g')$. Moreover, we should note that for each internal gate

  % We show that for all $g \in G$, $C_\equiv [\gamma \mathcal{A}]([g]) =
  % C[\gamma
  % \mathcal{A}](g)$ by induction on the structure of the circuit. Suppose $g
  % \in
  % G$ is an input gate then, since every input gate is part of a singleton
  % equivalence class, we have that $C /_\equiv [\gamma \mathcal{A}]([g]) =
  % C[\gamma \mathcal{A}](g)$. Suppose $g \in G$ is an internal gate. Let $h \in
  % [g]$ such that $L /_\equiv ([g]) = L(h)/_\equiv$. Then $(L/_\equiv)^{\gamma
  % \mathcal{A}}([g])(x) = C /_\equiv[\gamma \mathcal{A}](L /_\equiv ([g])(x)) =
  % C [\gamma \mathcal{A}](L(h)(x)) = L^{\gamma \mathcal{A}}(h)(x) \equiv
  % L^{\gamma \mathcal{A}}(g) \circ \lambda (x)$ for some $\lambda \in \aut(g)$.
  % But then, since $\Sigma (g)$ is a structured function, we have that
  % $\Sigma(g)((L^{\gamma \mathcal{A}}(g) \lambda)) = \Sigma(g)(\L^{\gamma
  % \mathcal{A}})$. It follows that $C /_\equiv [\gamma\mathcal{A}]([g]) =
  % \Sigma /_\equiv ((L/_\equiv)^{\gamma mathcal{A}}([g])) = \Sigma (L^{\gamma
  % \mathcal{A}}(g)\lambda) = \Sigma (L^{\gamma \mathcal{A}}(g)) = C[\gamma
  % \mathcal{A}](g)$. It follows that $C/_\equiv [\gamma \mathcal{A}]
  % (\Omega/_\equiv (\vec{a})) = C [\gamma \mathcal{A}](\Omega (\vec{a}))$ for
  % all
  % $a \in [n]^q$. It follows that $C_{\equiv}$ and $C$ compute the same
  % function.

  % Suppose $C$ is symmetric. Suppose $C$ is symmetric. We have from For $\sigma
  % \in \sym_n$ let $\pi \in \aut(C)$ be an extension of $\sigma$. It can be
  % shown
  % that $\pi$ is invariant under $\equiv$, and hence we have that $\pi
  % /_{\equiv}$ is a function. Since each gate that is either an input or output
  % gate is a member of a singleton equivalence class we only need to check the
  % symmetry condition for internal gates. Suppose $g$ is an internal gate then
  % $\pi /_{\equiv} L /_{\equiv}([g]) (x) = [\pi L(g) (x)] = [L(\pi g) (\lambda
  % x)] = L([\pi g]) (\lambda x) = L(\pi /_{\equiv} [g]) (\lambda x)$ for some
  % $\lambda \in \aut(g)$. It follows that $\pi /_{\equiv}$ is an automorphism
  % of
  % $C_{\equiv}$ extending $\sigma$, and so $C_{\equiv}$ is symmetric.

  % Let $[g], [g'] \in G/_{\equiv}$. Suppose $[g] \equiv [g']$. If $g$ is an
  % input
  % or output gate we have that $g = g'$. Suppose $g$ is an internal gate. Then
  % there exists $h \in [g]$ and $h' \in [g']$ such that $L /_\equiv ([g]) =
  % L(h)
  % /_\equiv$ and $L /_\equiv ([g']) = L(h') /_\equiv$. We have that
  % $L_{\equiv}([g])$ is isomorphism-equivilent to $L_{\equiv}$

  % Let $g \in G$. Since every gate in $G /_{\equiv}$ is part of a singleton
  % equivalence class.

  % Then for each gate $g,
  % g' \in G$ such that $g \equiv g'$ we have that $C[\gamma\mathcal{A}](g) =
  % C[\gamma \mathcal{A}](g')$. If $g$ is an input gate we have that
  % $C[\gamma\mathcal{A}](g) = C /_\eqiv [\gamma \mathcal{A}]([g])$. Suppose
  % $[g] \in G /_{\equiv}$ is an internal gate. Let $L^{\gamma}([g]) : \ind(g)
  % \rightarrow \{0,1\}$ be defined by $L^{\gamma}([g]) (x) = C[\gamma
  % \mathcal{A}]([g])$
\end{proof}

It is worth noting that if $C$ is a transparent circuit we can compute a
quotient of $C$ in time polynomial in the size of $C$. Since the circuit is
transparent we can compute the syntactic-equivalence classes of $C$ in
polynomial time (see Lemma~\ref{lem:transparent-syntactic-equiv}). Picking a
representative of each equivalence class and wiring up the circuit in the
obvious way then yields the desired quotient circuit.

We now show that transparent circuits can be transformed in polynomial time into
equivalent circuit with unique labels, and hence unique extensions (see
Lemma~\ref{}), and that this transformation preserves important properties of
the circuit.

\begin{lem}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
  $(\mathbb{B}, \rho)$-circuit. There is an algorithm that that takes in such a
  circuit and outputs a $(\mathbb{B} \cup \mathbb{B}_{\std}, \rho)$-circuit $C'$
  such that $C$ and $C'$ compute the same function, $C'$ has unique labels, and
  if $C$ is symmetric then $C'$ is symmetric. Moreover, this algorithm runs in
  time polynomial in the size of the input circuit.
  \label{lem:transparent-unique}
\end{lem}
\begin{proof}
  Let $C_0 := \langle G_0, \Omega_0, \Sigma_0, \Lambda_0, L_0 \rangle$ be the
  quotient of $C$. If $C_0$ does not contain the constant gates $g_0$ and $g_1$
  such that $\Sigma(g_0) = 0$ and $\Sigma (g_1) = 1$ we construct a new circuit
  from $C_0$ by adding these gates. We abuse notation and also call this new
  circuit $C_0$. The addition of these constant gates to the circuit does not
  alter the function computed by the circuit, nor does it effect the symmetry of
  the circuit or weather it has unique labels.

  The proof proceeds by first defining a circuit $C_1$ from $C_0$ and then
  defining $C'$ from $C_1$. We then show that each of these constructions
  preserves the relevant circuit properties and that $C'$ has unique labels.

  We will define $C_1$ from $C_0$ by adding a designated gate that always
  evaluates to $1$ and which is part of a singleton syntactic-equivalence class,
  and then adding a wire from that gate to each $\AND$-gate in the circuit. This
  process ensures that each $\AND$-gates in $C_1$ has a fan-in of at least two.
  The construction of $C'$ from $C_1$ involves adding in a number of
  single-input $\AND$-gates, and so the construction of $C_1$ will allow us to
  distinguish these new gates from those in $C_1$.

  We now define the circuit $C_1$ formally. Let $C_1 := \langle G_1, \Omega_1,
  \Sigma_1 , \Lambda_1, L_1 \rangle$ be defined as follows. Let $G_1 = G_0
  \uplus \{ g_\lor\}$. Let $\Omega_1 = \Omega_0$ and $\Lambda_1 = \Lambda_0$.
  Let $g \in G_1$. If $g = g_\lor$ then $\Sigma_1 (g) = \lor[2]$, $L_1(g)(1) =
  g_0$, and $L_1(g)(2) = g_1$. If $g \in G_0$, $\Sigma(g) = \lor[2]$ and $H_g =
  \{g_0, g_1\}$ then $\Sigma_1 (g) = \lor[3]$, $L_1(g)(1) = L_0(g)(1)$,
  $L_1(g)(2) = L_0(g)(2)$, and $L_1(g)(3) = g_\lor$. If $g \in G_0$ and $g =
  \land[k]$ for some $k \in \nats$ then $\Sigma_1(g) = \land[k+1]$ and
  $L_1(g)(i) = L_0(g)(i)$ for all $i \in [k]$ and $L_1(g)(k+1) = g_\lor$.
  Otherwise let $\Sigma_1(g) = \Sigma_0(g)$ and $L_1(g) = L_0(g)$.

  More informally, we define $C_1$ from $C_0$ by adding in an $\OR$-gate
  $g_\lor$ that always evaluates to one, and then adding a wire from that gate
  to all $\AND$-gates in the circuit, and also a wire from $g_\lor$ to another
  $\OR$-gate in order to ensure that $g_\lor$ is part of a singleton
  syntactic-equivalence class in $C_1$. The important point to note is that each
  $\AND$-gate in $C_1$ has fan-in at least two, a property we will use to
  construct $C'$. We now show that the construction of $C_1$ preserves the
  relevant circuit properties.

  % We have defined $C_1$ from $C_0$ by in a gate $g_\lor$ that always evaluates
  % to $1$ and then adding a wire from that gate to each $\AND$-gate in the
  % circuit. This process ensures that each $\AND$-gates in $C_1$ has a fan-in
  % of at least two. The construction of $C'$ from $C_1$ involves adding in a
  % number of single-input $\AND$-gates, and so the construction of $C_1$ will
  % allow us to distinguish these new gates from those in $C_1$.

  % We have constructed $C_1$ from $C_0$ by adding in a gate $g_\lor$ and then
  % adding a wire from $g_\lor$ to each $\AND$-gate in the circuit and each gate
  % two-input $\OR$-gate with the same children as $g_\lor$. Since $g_\lor$
  % always evaluates to $1$, adding as an input to each $\AND$-gate (or the
  % $\OR$-gate) has no effect on the evaluation of the circuit.

  It is easy to see that if $C$ has order $n$ then $C_0$ has order $n$ and so
  $C_1$ has order $n$. Let $\mathcal{A}$ be a $\rho$-structure of size $n$ and
  let $\gamma$ be a bijection from the universe of $\mathcal{A}$ to $[n]$. We
  have that $C_1[\gamma \mathcal{A}](g_\lor) = 1$. We constructed $C_1$ from
  $C_0$ by adding a single wire from $g_\lor$ to each $\AND$-gate and each
  two-input $\OR$-gate with only the two constant gates as children. Notice that
  if $g$ is a two-input $\OR$ gate in $C_0$ with the two constant gates as
  children, then since $g$ has $g_1$ as a child and $g$ is an $\OR$-gate
  $C_0[\gamma \mathcal{A}](g) = C_1[\gamma \mathcal{A}](g) = 1$. It can be shown
  by induction that if $g \in G_1 \setminus \{g_\lor\}$ then $C_0 [\gamma
  \mathcal{A}](g) = C_1[\gamma \mathcal{A}](g)$. Since $\Omega_1 = \Omega_0$, it
  follows that $C_0$ and $C_1$ compute the same function. We thus have from
  Lemma~\ref{lem:quotient-circuits-preserve} that $C$ and $C_1$ compute the same
  function.

  Suppose $C$ is symmetric. From Lemma~\ref{lem:quotient-circuits-preserve} it
  follows that $C_0$ is symmetric. Let $\sigma \in sym_n$ and let $\pi_0 \in
  \aut(C_0)$ be an extension of $\sigma$. We define a bijection $\pi_1 : G_1
  \rightarrow G_1$ such that $\pi_1 (g) = \pi_0(g)$ for all $g \in G_0$ and
  $\pi_1 (g_\lor) = g_\lor$. It is easy to see that $\pi_1$ is an automorphism
  of $C_1$ extending $\sigma$. It follows that $C_1$ is symmetric.

  We have from Lemma~\ref{lem:quotient-circuits-preserve} that $C_0$ has trivial
  syntactic-equivalence classes. Since $g_\lor$ is the only two input $\OR$-gate
  with exactly the two constant gates as children, it follows that $g_\lor$ is
  contained in a singleton syntactic-equivalence class. It can be shown by
  induction that if $g, g' \in G_0$ are syntactically equivalent in $C_1$ then
  they must be syntactically-equivalent in $C_0$. It follows that if $g$ and
  $g'$ are syntactically-equivalent in $C_1$ then $g = g'$. We thus have that
  $C_1$ has trivial syntactic-equivalence classes.

  Let $C' := \{G', \Omega', \Sigma' \Lambda' L'\}$ be defined as follows. For
  each $h \in G_1$ let $c^h_g := \vert L_1(g)^{-1}(h) \vert$ if $h \in H_g$ and
  $c^h_g := 0$ otherwise. For each $h \in G_1$ let $c^h$ be the maximum of
  $c^h_g$ for $g \in G_1$. For each $h \in G_1$ if $c^h > 1$ let $G_h :=
  \{g^{h}_{1}, ldots, g^h_{c_h-1}\}$ otherwise let $G_h := \emptyset$. Let
  $G_{\land} := \biguplus_{h \in G_1} G_h$ and $G' = G_{\land} \uplus G_1$. Let
  $\Omega' = \Omega_1$ and $\Lambda' = \Lambda_1$. For $g \in G'$ if $g \in G_1$
  let $\Sigma'(g) = \Sigma_1(g)$ and otherwise let $\Sigma'(g) = \land[1]$. For
  each $g \in G_1$ and $h \in H_g$ let $\{x^{h,g}_0, x^{h,g}_1 ,\ldots,
  x^{h,g}_{c^h_g - 1}\} := L_1(g)^{-1}(h)$ be a fixed ordering of the set
  $L_1(g)^{-1}(h)$. Let $g \in G'$. If $g \in G_1$ and $x \in \ind(g)$ then
  there exists $h \in H_g$ and $i \in \{0, \ldots , c^h_g -1\}$ such that $x =
  x^{h,g}_i$, and we let $L'(g)(x) = h$ if $i = 0$ and $L'(g)(x^{h,g}_i) =
  g^h_i$ otherwise. If $g \in G_{\land}$ then $g = g^h_i$ for some $h \in G_1$
  and $i \in [c^h_g]$, and we let $L'(g)(1) = h$ if $i = 1$ and $L'(g)(1) =
  g^h_{i-1}$ otherwise.

  The construction ensures that $C'$ has injective labels. Let $g \in G_1$. In
  order to avoid confusion we let $H_g$ be the set of children of $g$ in $C_1$
  and $H_g'$ be the set of children of $g$ in $C'$. If $g' \in G_1$ we let $g
  \equiv g'$ denote syntactic-equivalence in $C_1$ and $g \equiv' g'$ denote
  syntactic-equivalence in $C'$.

  \begin{claim}
    $C'$ has trivial syntactic-equivalence classes.
  \end{claim}
  \begin{proof}
    We prove this result by induction on depth. Let $g \in G'$. If $g$ has depth
    $0$ then $g$ is an input gate and so $[g] = \{g\}$. Let $g \in G'$ be an
    internal gate in $C'$ and suppose for each gate $h$ of depth less than $g$
    we have that $[h] = \{ h \}$. Let $g' \in G'$ and suppose $g \equiv' g'$. We
    now show that $g = g'$, and so prove the claim. Since $g \equiv' g'$ it
    follows that $\Sigma (g) = \Sigma(g')$ and both $g$ and $g'$ have the same
    depth. Moreover, from the inductive hypothesis, we have that there exists
    $\lambda \in \aut(g)$ such that for all $x \in \ind(g)$, $L'(g) (x) =
    L'(g')(x)$. It follows that $H_{g}' = H_{g'}'$. Moreover, from the inductive
    hypothesis the children of $g$ and $g'$ must be contained in singleton
    syntactic-equivalence classes, and so , since $C'$ has injective labels, it
    follows that $g$ and $g'$ have unique labels in $C'$.

    % Suppose $g = g_\lor$. Then $H_g = H_g' = \{g_0, g_1\} = H_{g'}'$ and
    % $\Sigma' (g) = \Sigma'(g') = \lor[2]$. But from the construction the only
    % two-input $\OR$-gate in $C_1$, and so $C'$, with children $\{g_0 , g_1\}$
    % is
    % $g$. It follows that $g = g'$.

    Suppose $g \in G_{\land}$. Then there exists $h \in G_1$ and $i \in [c^h -
    1]$ such that $g = g^h_i$. Suppose $g' \in G_1$. Then $\Sigma'(g) =
    \land[1]$. But, from the construction of $C_1$, there are no single-input
    $\AND$-gates in $G_1$. It follows $\Sigma'(g') \neq \Sigma'(g)$ and so $g'
    \not\equiv' g$, a contradiction, and so we must have $g' \in G_{\land}$. If
    $i = 1$ then $\{ h \} = H_g' = H_{g'}'$. Since the only gate in $G_\land$
    that has $h$ as a child gate is $g^h_1$, it follows that $g = g^h_1 = g'$.
    If $i > 1$ then $\{g^{h}_{i-1}\} = H_g' = H_{g'}'$. Since $g^h_i$ is the
    only gate in $G_\land$ that has $g^h_{i-1}$ as a child gate, we have $g =
    g^h_i = g'$. It follows that if $g \in G_\land$ then $g = g'$.

    Suppose $g \in G_1$. We have already shown that if $g' \in G_\land G_1$ then
    $g \not\equiv' g'$, a contradiction, and so we must have $g' \in G_1$. Since
    $g \equiv' g'$ there exists $\lambda \in \aut(g)$ such that for all $x \in
    \ind(g)$, $L'(g)(\lambda x) = L'(g')(x)$. From the construction, we have
    that for all $x \in \ind(g)$ and $h \in G_1$, $L'(g)(x) \in \{h, g^h_1 ,
    \ldots, g^h_{c^h_g -1}\}$ if, and only if, $L_1(g)(x) = h$. Suppose $g$ is
    not a symmetric gate. Since $C$ is transparent, $C_0$ is transparent and so
    $C_1$ is transparent. It follows that for all $h \in H_g$, $H_g = H_{g'}$,
    and $c^h_g = 1 = c^h_{g'}$. It follows that for all $x \in \ind(g)$, there
    exists a unique $h \in G_1$ such that $L_1(g)(\lambda x) = L'(g)(\lambda x)
    = L'(g')(x) = L_1 (g')(x) = h$. It follows that $g \equiv g'$ and so $g =
    g'$. Suppose $g$ is a symmetric gate. Let $x \ind(g)$ and $h = L_1(g)(x)$.
    If $L'(g)(\lambda x) = L'(g')(x)= h$ then $L_1(g)(\lambda x) = h$ if, and
    only if, $L'(g)(\lambda x ) = h* = L'(g')(x)$, where $h* = h$ or $h* =
    g^{h}_i$, for some $i \in [c^h_g -1]$, if, and only if, $L_1(g) (x) = h$. It
    follows that for all $x \in \ind(g)$, $L_1 (g) (\lambda x) = L_1 (g)(x)$,
    and so $g \equiv g'$ and so $g = g'$.

    % It follows that for all $g \in G'$, $[g] = \{g\}$. The result follows.

    % Suppose $g \in G_0$. If $g$ is a non-symmetric gate then $g$ has unique
    % labels in $C_0$ and so has unique labels in $C_1$. It follows that for all
    % $h \in H_g$, $c^h_g = 1$, $g$ has injective labels in $C'$ and so, using
    % the
    % inductive hypothesis, $g$ has unique labels. Since $g \equiv' g'$ we also
    % have that $g'$ has unique labels.

    % It is easy to show that for all $h, g \in G_1$, if $W_t(h,g)$ in $C_1$
    % then
    % $W_t(h,g)$ in $C'$. We prove this result by induction on depth. Suppose
    % $g$
    % and $g'$ have depth $0$ in $C'$ then $g$ and $g'$ are input gates, and so
    % $g
    % \equiv' g'$ if, and only if, $g = g'$ if, and only if, $g \equiv g'$.
    % Suppose $g, g' \in G_1$ are internal symmetric gates and for all $h , h'
    % \in
    % G_1$ of depth less than $g$ or $g'$ in $C'$ $h \equiv h'$ if, and only if,
    % $h \equiv' h'$. Suppose $g \equiv g'$. Then there exists $\lambda \in
    % \aut(g)$ such that for all $x \in \ind(g)$, $L_1(g)(x) \equiv
    % L_1(g')(\lambda x)$. If $H_g'\cup \H_{g'}' \subseteq G_1$ then the result
    % follows obviously from the inductive hypothesis. For each $h \in H_g$ and
    % $x
    % \in L(g)^{-1}(h)$ if $c^h_g = 1$ then let $\lambda' x = x$ and if $c^h_g >
    % 1$ and if $x = x^{h,g}_i$ for some $i \in [c^h_g - 1]$ then $\lambda' x =
    % x^{h', g'}_i$ where $h' = L_1(g')(\lambda x)$. It can be shown that
    % $\lambda'$ is a bijection on $\ind(g)$. Since $g$ and $g'$ are symmetric
    % gates it follows that $\lambda' \in \aut(g)$...
  \end{proof}

  Since $C'$ has injective labels and trivial syntactic-equivalence classes it
  follows $C'$ has unique labels.

  We have already shown that if $C$ is symmetric then $C_1$ is symmetric. We now
  show that if $C_1$ is symmetric then $C'$ is symmetric. Suppose $C_1$ is
  symmetric. Let $\sigma \in \sym_n$ and let $\pi_1 \in \aut(C_1)$ be an
  extension of $\sigma$. We define the function $\pi' : G' \rightarrow G'$ as
  follows. Let $g \in G'$. If $g \in G_1$ then $\pi'(g) = \pi_1(g)$, otherwise
  $g \in G_\land$, and so there exists $h \in G_1$ and $i \in [c^h - 1]$ such
  that $g = g^h_i$, let $\pi'(g) = g^{\pi_1 h}_i$. It is easy to show that
  $\pi'$ is an automorphism of $C'$ extending $\sigma$.
